
\section*{\underline{Title:} STAR Online Judge - The Programming Contest Platform\\}
\vspace{50pt}
\section*{\underline{\\Abstract:}}
The online judge has several features, to name a few; the user can both participate and host
contest. Solve archived problems, search problems by tags or category be it problem type or
problem setter. The user can also check their submission status in real-time. Also user can see
their progress which is displayed through a graph.

\section*{\underline{Objectives:}}
Build an online competitive programming platform, to host contests; that can support concurrent
submissions by users. Keep track of user's progress and update submission status in real-time.

\section*{\underline{Scope:}}
The online judge can support several concurrent submissions by the participants, the rest will be
placed in queue, and judged accordingly.

\section*{\underline{Functionalities:}}
\begin{itemize}
  \item Host programming contests
  \item Real-time update of submission status
  \item Keep track of user’s progress
  \item Participate in replay and mock contest
  \item Categorized problems
  \item Practise problems from archive
  \item Search for problems through tags and category
\end{itemize}

\section*{\underline{Preferred Technology:}}
\begin{itemize}
  \item Coding: PHP, Javascript, GoLang, Java
  \item Sandboxing: Linux
  \item Development \& Testing Environment: Brackets, PHPStorm , XAMPP
  \item Design and Mockup: Photoshop
  \item UML Modelling: StarUML
  \item Hosting: Virtual Private Server(VPS)
  \item Documentation: \LaTeX
\end{itemize}


\section*{\underline{Conclusion:}}
Our idea is to develop an Online Judge from scratch. To inspire the upcoming software
engineers, who wish to pursue how the software architecture behind an online judge is designed,
as well as how it is developed. If we get proper support from the authority then we can update
the Application features in future. It will be a challenging task for us to accomplish our goal, but
we will strive to achieve our goals.
